The \Prob

### 2013-03-07 bikes/bikes.tex
bikes touchups

The \prob~has far-reaching implications in many fields, including comestibility theory~\cite{comestibility}, deep-space navigation~\cite{arkanoid}, maximum-jerk motion planning~\cite{jerk,jerk2}, and pop-math brainteasers.

@@

These are some more tables we drew when deciding whether Theorem~\ref{thm:cont} was really true, and they were too colorful not to include.

>>>>

The \prob~has far-reaching implications in many fields, including comestibility theory~\cite{comestibility}, deep-space navigation~\cite{arkanoid}, maximum-jerk motion planning~\cite{jerk2}, and pop-math brainteasers.

@@

These are some more tables we drew when deciding whether Theorem~\ref{thm:cont} was even true at all, and they were too colorful not to include.
